---
title: "727 Final Project"
subtitle: "Socioeconomic Influence on the Usage and Perception of Public Libraries"
author: "Sol Rabine"
date: "2023-12-13"
output: pdf_document
references:
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(DBI)
library(plyr)
library(dbplyr)
library(bigrquery)
library(readxl)
library(ggplot2)
library(stringr)
library(stringr)
library(ggmap)
library(dplyr)
```

<https://github.com/rabine13/SURVMETH-727>

```{r}
adi <- read_csv("~/Desktop/SURVMETH 727/Final project/ustable.csv")
atf <- read_csv("~/Desktop/SURVMETH 727/Final project/usatf.csv")
pls <- read_csv("~/Desktop/SURVMETH 727/Final project/uspls.csv")
```

# The Question

## Across the US, libraries are one of the few places that offer their space and resources to the public for free. This project seeks to examine the differences in how libraries are seen and used by theur communities. Given that it is easier than ever to access information from the internet, are libraries still seen as an important hub of knowledge? Do people from different socioeconomic backgrounds view their library differently?

# The Data

## Data for this project comes from from three datasets. The first is the 2018 Area Deprivation Index, which I accessed from the Google Bigquery API. The Area Deprivation Index (ADI) is an evaluation of socioeconomic status compiled from multiple measures in the American Community Survey. I was unable to find a definitive explaination of how the index is created. This dataset contains an ADI measure for 32664 US zip codes.

## Next is the 2018 Public Libraries Survey, a national census of public libraries in the US and its territories. The survey is conducted by the Institute of Museum and Library Services. The survey is administered to central libraries, who report on all the branches in their system. This dataset (pls) contains robust data about a library system's visitors, employment, revenue, use of materials, and more. This data is linked to the address of the central library in each system. This dataset covers 9261 central libraries. I was able to match 7642 to the ADI of their zipcode.

## The last dataset is from a survey called Awareness to Funding: Voter Perceptions and Support of Public Libraries in 2018 (atf). The survey is conducted by OCLC and the American Library Association. This survey covers 2914 individuals across the country and asks questions about their use of libraries, impression of them, and support of them.

## The data has been merged into 4 different datasets to get the most possible cases for comparison. All datasets were merged using zip codes. The datasets are as follows:

### fullset: contains 819 cases matching public library survey, ADI, and awareness to funding data

### plsadi: contains 7642 cases matching public library data with the ADI of the central library's zipcode. Used for comparative measures of ADI with library hours, visitors, wifi usage, and service area population.

### plsatf: contains 997 cases matching individuals in the Awareness to Funding survey with the central library in their zipcode. Used to compare perceptions of libraries with measures of their use.

### atfadi: contains 2642 cases matching individuals in the Awareness to Funding survey with the ADI of their zipcode. Used to compare usage and perceptions of libraries for individuals in communities with different socioeconomic status.

```{r Final merge and clean}
atf$Q1 <- gsub('1 Unsatisfactory', '1', atf$Q1)
atf$Q1 <- as.numeric(atf$Q1)
plsadi <- merge(pls, adi, by.x = "ZIP", by.y = "zipcode", all= FALSE)
plsatf <- merge(pls, atf, by.x = "ZIP", by.y = "ZIPCODE", all = FALSE)
atfadi <- merge(atf, adi, by.x = "ZIPCODE", by.y = "zipcode", all = FALSE)


fullset <- merge(plsadi, atf, by.x = "ZIP", by.y = "ZIPCODE", all = FALSE)

#remove geo_id, description, year

fullset$geo_id <- NULL
fullset$description <- NULL
fullset$year <- NULL

names(plsadi)[35] <- 'ADI'
names(fullset)[32] <- 'ADI'
names(atfadi)[44] <- 'ADI'

```

\newpage

# Mapping the libraries

## The purple points on the map represent central libraries that were matched to both their ADI and an individual's ATF responses.

## The green points on the map represent central libraries that were matched only to ADI.

## The blue points on the map represent libraries in the PLS dataset that were not matched to the other datasets.

I was unable to retrieve map data for Alaska, Hawaii, American Samoa,
Northern Mariana Islands, Guam, Puerto Rico, and US Virgin Islands so
they have been excluded from this map.

```{r}
all_states <- map_data("state")
```

```{r Map comparing libraries in the full dataset and the ATF dataset}
#remove Alaska and Hawaii 
pls_continent <- filter(pls, !(STABR %in% c('AK', 'HI', 'AS', 'MP', 'GU', 'PR', 'VI')))
plsadi_continent <- filter(plsadi, !(STABR %in% c('AK', 'HI', 'AS', 'MP', 'GU', 'PR', 'VI')))
fullset_contient <- filter(fullset, !(STABR %in% c('AK', 'HI', 'AS', 'MP', 'GU', 'PR', 'VI')))
usmap <- ggplot()+
  geom_polygon(data = all_states, aes(x=long, y=lat, group = group), fill = "grey", color = "black") + 
   geom_point(data = pls_continent, aes(x=LONGITUD, y=LATITUDE), color = "blue") +
  geom_point(data = plsadi_continent, aes(x=LONGITUD, y=LATITUDE), color = "darkgreen") + 
  geom_point(data = fullset_contient, aes(x= LONGITUD, y= LATITUDE), color = "purple") 
usmap
 # ggsave("usmap.png", device = "png", width = 5, height = 5)
```

\newpage

# Exploration

First, I wanted to look for a correlation between population of a
library's service area and the visits per year. This analysis uses just
the PLS data since merging with other datasets reduced the number of
cases. There is a large variation in the sizes of library systems in
this dataset.

```{r population vs visits}
plot <- ggplot(pls, aes(x=POPU_LSA, y=VISITS))+
  geom_point(color = "darkgreen", na.rm= TRUE)+ 
  labs(x='Population of Service Area', y= 'visits', title = "Visits by Population of Service Area", caption = "Dataset: PLS")
plot
#ggsave("plot.png", device = "png", width = 8, height = 5)

cor.test(pls$POPU_LSA,pls$VISITS, 
         alternative="greater", 
         method= "pearson")
```

Understandably, there is a significant positive correlation.

```{r}
#also maybe weight by branches
highvisit <- plsadi %>%
  filter(VISITS > 5000000)
```

I next wanted to examine if library visitorship has a correlation with
ADI. I expected that there would be a positive correlation, that
libraries in areas with higher ADI (worse socioeconomic status) would
have more visitors. The expectation being that people with less access
to internet, education systems, and learning resources might go to the
library more to make use of their public resources.

```{r Visits vs ADI}
plot <- ggplot(plsadi, aes(x=ADI, y=VISITS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Visits', title = "Visits by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI, plsadi$VISITS, 
         alternative="greater", 
         method= "pearson")
```

There is no significant correlation. I decided to see if there was a
difference if I looked at the percent of population that had visited.

```{r percent Visits vs ADI}
plsadi$PERCENT_VISIT <- (plsadi$VISITS/plsadi$POPU_LSA)*100

plot <- ggplot(plsadi, aes(x=ADI, y=PERCENT_VISIT))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Percent of Population that Visited', title = "Percent Visited by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$PERCENT_VISIT, 
         alternative="greater", 
         method= "pearson")

```

I noticed three outliers that seemed to have a very low population but
high number of visits:

-   The Lake Minchumina Community Library with a service area population
    of 9 and 2071 visits in 2018.

-   The Adams-Pratt Oakland County Law Library with a service area
    population of 19 and 28700 visits in 2018.

-   The Round Top Family Library with a service area population of 91
    and 24531 visits in 2018.

I could find no clear reason for the discrepancy so I did the test with
these outliers removed.

```{r}
plsadiclean <- plsadi[-c(7623,2843, 6536),]
plsadiclean$PERCENT_VISIT <- (plsadiclean$VISITS/plsadiclean$POPU_LSA)*100

plot <- ggplot(plsadiclean, aes(x=ADI, y=PERCENT_VISIT))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Percent of Population that Visited', title = "Percent Visited by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$PERCENT_VISIT, 
         alternative="greater", 
         method= "pearson")

```

There still is no significant correlation, but the distribution looks
much better. \pagebreak Next, I looked at the hours each branch is open,
compared to ADI. I removed problem cases where there were zero branch or
central libraries reported.

```{r Hours library is open compared to ADI of its zipcode}
plsadi$HRS_BRANCH <- plsadi$HRS_OPEN/(plsadi$CENTLIB+plsadi$BRANLIB)
#remove problem cases
plsadiclean <- plsadi[-c(802,1005, 1816, 4124, 4206, 4375, 6680, 6688, 6915, 6918, 6936, 6937, 6938, 6947, 6948, 7023, 5328),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=HRS_BRANCH))+
  geom_point(na.rm= TRUE)
plot + labs(title = "Branch Hours by ADI", x='Area Deprivation Index', y= 'Hours Open Per Branch', caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI, plsadiclean$HRS_BRANCH, 
         alternative="greater",
         method= "pearson")

```

There is no significant correlation.

\pagebreak

I next compared the hours each branch is open with the population they
serve.

```{r}
plsadi$HRS_BRANCH <- plsadi$HRS_OPEN/(plsadi$CENTLIB+plsadi$BRANLIB)
#remove problem cases
plsadiclean <- plsadi[-c(802,1005, 1816, 4124, 4206, 4375, 6680, 6688, 6915, 6918, 6936, 6937, 6938, 6947, 6948, 7023, 5328),]

plot <- ggplot(plsadiclean, aes(x=HRS_BRANCH, y=POPU_LSA))+
  geom_point(na.rm= TRUE)
plot + labs(title = "Branch Hours by Population", x='Hours Open Per Branch', y= 'Population Service Area', caption = "Dataset: plsadi")

cor.test(plsadiclean$POPU_LSA, plsadiclean$HRS_BRANCH, 
         alternative="greater",
         method= "pearson")
```

```{r}
notable <- plsadi %>%
  filter(HRS_BRANCH > 6000)
```

There is a weak but significant positive correlation.

Finally, I decided to see if the registered library users correlated
with ADI, again expecting more users in higher ADI areas. One issue I
anticipated with this measure is that registered users may not actually
capture all library users. Most libraries require a mailing address when
registering. This may exclude unhoused people from the registration
data, even if they visit their library regularly.

```{r}
plot <- ggplot(plsadi, aes(x=ADI, y=REGBOR))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Registered users', caption = "Dataset: plsadi", title = "Registered Users by ADI")


cor.test(plsadi$ADI,plsadi$REGBOR, 
         alternative="greater", 
         method= "pearson")

plsadi$PERCENT_USRS <- plsadi$REGBOR/plsadi$POPU_LSA *100

plot <- ggplot(plsadi, aes(x=ADI, y=PERCENT_USRS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Percent of Population Registered Users', title = "Percent Registered Users by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$PERCENT_USRS, 
         alternative="greater", 
         method= "pearson")


```

There is no significant correlation with the number of registered users
or the percent that are registered users. There was one unanticipated
issue with this analysis; the percent of population that are registered
users is frequently over 100%. My assumption is that these libraries
have not removed registrations for people who have moved or passed away,
leading to this overestimation.

\pagebreak

Next, we look at wifi use and ADI. I expect that there will be a
positive correlation, more people using the wifi in more deprived areas.

```{r}
plot <- ggplot(plsadi, aes(x=ADI, y=WIFISESS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi sessions', title = "Wifi Sessions by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$WIFISESS, 
         alternative="greater", 
         method= "pearson")

plsadi$wifi_visit <- plsadi$WIFISESS/plsadi$VISITS

plot <- ggplot(plsadi, aes(x=ADI, y=wifi_visit))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi Sessions Per Visit', title = "Wifi Sessions Per Visit by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$wifi_visit, 
         alternative="greater", 
         method= "pearson")

```

There was no correlation between wifi use and ADI before weighting by
total visits.

There is a very small but significant positive positive correlation
between ADI and wifi uses per visit. Meaning, as ADI increases, the
number of people who use the wifi during their visit increases. One
possible explanation is that people in people in more deprived areas are
going to the library to use the wifi because they do not have access at
home. This is expected, but I am surprised the correlation was not
stronger.

I noticed that the library with the most wifi sessions per visit was the
Madera County Law Library, with 368.54 wifi uses per visit. This seems
like a reporting error, so I went ahead and excluded it.

```{r}
plsadiclean <- plsadi[-c(7261),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=WIFISESS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi sessions', title = "Wifi Sessions by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$WIFISESS, 
         alternative="greater", 
         method= "pearson")


plsadiclean$wifi_visit <- plsadiclean$WIFISESS/plsadiclean$VISITS

plot <- ggplot(plsadiclean, aes(x=ADI, y=wifi_visit))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi sessions Per Visit', title = "Wifi Sessions Per Visit by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$wifi_visit, 
         alternative="greater", 
         method= "pearson")

```

Having removed this outlier, the correlation between ADI and Wifi
sessions per visit is slightly larger and more statistically
significant.

\pagebreak

I also wanted to look at the relationship between staff salaries and
ADI. I expected that libraries in areas with higher ADI would pay their
staff less. I removed cases where salaries were reported as 0 or NA.

```{r}
plsadiclean <- plsadi[-c(5424, 7260, 7193, 7363, 7222),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=SALARIES))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Total staff expenditures', title = "Total Staff Expenditures by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$SALARIES, 
         alternative="greater", 
         method= "pearson")
```

Looking at the total staff expenditures, there is no significant
correlation.

\pagebreak

Next I divided the total staff expenditures by the number of staff
members to get an average salary per employee. I removed cases that were
0 or NA, and cases where the resulting average was greater than 200,000.

```{r}
plsadi$SALARY_EMP <- plsadi$SALARIES/plsadi$TOTSTAFF
plsadiclean <- plsadi[-c(5424, 7260, 7193, 7363, 7222, 1738),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=SALARY_EMP))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Salary per employee', title = "Salary Per Employee by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$SALARY_EMP, 
         alternative="greater", 
         method= "pearson")

```

There is no significant correlation

\pagebreak

# Visitors and non visitors

There were much more library visitors than non-visitors in the ATF data

```{r Number of non visitors and visitors in the ATF data}
count(atf, vars = 'VISIT')
```

734 did not visit a library in the past year

2179 did visit a library in the past year

Looking at the main topic of this report, I was curious if visitorship
varied by ADI.

```{r whether sample member had visited vs adi of their zip}
plot <- ggplot(atfadi, aes(x=as.factor(VISIT), y=ADI, group = VISIT))+
  geom_boxplot(na.rm= TRUE) +
  labs(x='Visited', y= 'Area Deprivation Index', title = "Comparing ADI of Visitors and Non-Visitors", caption = "Dataset: atfadi")+
  scale_x_discrete(labels = c("0" ="No", "1"="Yes"))
plot

```

Comparing the ADI of sample members who reported visiting their library
and those who did not, we see that those who visited tended to live in
areas with a slightly higher ADI.

Despite this, the pattern of incomes for visitors and non-visitors was
roughly the same, as shown below:

```{r}
ggplot(atf, aes(as.factor(VISIT))) + 
  geom_bar(aes(fill = as_factor(SS3)), position = "dodge")+
  scale_x_discrete(labels = c("0"="No", "1"="Yes"))+
  labs(x='Visited in Past Year', y= 'Count', title = "Income of ATF Sample Members", caption = "Dataset: atf")+
scale_fill_discrete(name = "Income", labels=c("1 Less than $20K", "2 $20K to $29K", "3 $30K to $39K", "4 $40K to $49K", "5 $50K to $59K", "6 $60K to $74K", "7 $75K to $99K", "8 $100K to $149K", "9 $150K or more"))
```

Next, I wanted to see if the income of individuals in the sample was
representative of their area. As shown below, sample members with high
income were on average from higher ADI (more deprived) areas. Based on
this, it is important to note these sample members may not be
representative of other people in their area.

```{r}

plot <- ggplot(atfadi, aes(x=as.factor(SS3), y=ADI, group=S8_31))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Income', y= 'Area Deprivation Index', caption = "Dataset: atfadi")+
 scale_x_discrete(labels = c("< $20K", "$20K to 
  $29K", "$30K to 
  $39K", "$40K to 
  $49K", "$50K to 
  $59K", "$60K to 
  $74K", "$75K to 
  $99K", "$100K to 
  $149K", "> $150K "))
plot
```

\pagebreak

Visitors tended to have a better impression of their library than
non-visitors.

```{r}
plot <- ggplot(atf, aes(x=as.factor(VISIT), y=as.factor(Q1), group=VISIT))+
  geom_boxplot(na.rm= TRUE) + 
  labs(x='Visited in past year', y= 'Overall Impression Local Library', title = "Impression of Library by Visitorship", caption = "Dataset: atf")+
   scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Unsatisfactory', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 An Excellent Library"))
plot

```

I was curious if this positive impression translated to material support
of their library, so I compared whether a respondent had visited their
library in the past year with their response to a likert scale asking if
the public library should be a high priority for allocating tax dollars.

```{r Visits vs funding priority}
plot <- ggplot(atf, aes(x=as.factor(VISIT), y=as.factor(Q9_1_5), group=VISIT))+
  geom_boxplot(na.rm= TRUE)+
 labs(x='Visited in past year', y= 'Top priority allocating tax dollars - Public Library', title = "Funding Priority by Visitorship", caption = "Dataset: atf") +
 scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot

#tax <- ggplot(atf, aes(as.factor(VISIT))) + 
  #geom_bar(aes(fill = as.factor(Q9_1_5)))+
 # scale_x_discrete(labels = c("0"="No", "1"="Yes"))+
 # labs(x='Visited in past year', y= 'Count')+
#scale_fill_brewer(palette = "PRGn",name = "Top priority allocating tax dollars - Public Library", labels=c("1 Strongly Disagree", "2", "3", "4", "5", "6", "7", "8", "9", "10 Strongly Agree"))

#print(tax)
#ggsave("tax.png", device = "png", width = 8, height = 5)
```

Those who have visited are much more supportive of allocating tax
dollars to the public library. The mean for visitors is 2 points higher
on the scale than for non visitors.

Those who have visited were also more supportive of increased taxes to
better fund their library.

```{r}
#add a cor test
plot <- ggplot(fullset, aes(x=as.factor(VISIT), y=as.factor(s6_b), group=VISIT))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Visited in past year', y= 'I would be willing to pay more in taxes if it meant 
       better funding for the local public library ',caption = "Dataset: fullset")+
  scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot

```

```{r}
plot <- ggplot(atf, aes(x=as.factor(VISIT), y=as.factor(s6_g), group=VISIT))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Visited in past year', y= "I don't support tax increases that fund services
       I don't use or benefit from",caption = "Dataset: atf")+
    scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot
```

There were neutral responses from both visitors and non-visitors to the
statement "I don't support tax increases that fund services I don't use
or benefit from." This statement is vague, so it is hard to draw a
meaningful conclusion about library support.

\pagebreak

I expected there would be a correlation between people's willingness to
fund their library and the library's revenue, but there was not.

```{r}
plot <- ggplot(plsatf, aes(x=as.factor(s6_b), y=TOTINCM, group=s6_b))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='I would be willing to pay more in taxes if it meant better 
            funding for the local public library ', y= 'Total operating revenue', caption = "Dataset: plsatf", title = "Willingness to Fund and Revenue")+
  scale_x_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly 
    Agree"))

cor.test(plsatf$s6_b, plsatf$TOTINCM, 
         alternative="greater", 
         method= "pearson")
```

I also expected a correlation between people's impression of their
library and its income, but found no significant correlation. This could
be good news, showing that even poorly funded libraries can rally the
support of their communities.

```{r}
plot <- ggplot(plsatf, aes(x=as.factor(Q1), y=TOTINCM, group=Q1))+
  geom_boxplot(na.rm= TRUE)+ 
  labs(x='Overall Impression Public Library', y= 'Total operating revenue', caption = "Dataset: plsatf", title = "Impression By Revenue")+
  scale_x_discrete(labels = c('1'= '1 Unsatisfactory', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 An 
    Excellent 
    Library"))
plot

cor.test(plsatf$Q1, plsatf$TOTINCM, 
         alternative="greater", 
         method= "pearson")
```

```{r}
plot <- ggplot(atfadi, aes(x=as.factor(Q14), y=ADI, group = Q14))+
  geom_boxplot(na.rm= TRUE) + 
  labs(x='Importance of a strong public library system', y= 'Area Deprivation Index', caption = "Dataset: atfadi")+         scale_x_discrete(labels = c('1'= '1 Not at 
      all Important', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Extremely 
  Important"))
  
plot

cor.test(atfadi$Q14, atfadi$ADI, 
         alternative="greater", 
         method= "pearson")
```

There is a small positive correlation between ADI and belief in the
importance of a strong public library system. Those who said a strong
library system was not important lived in lower ADI areas on average.
Perhaps those who live in these areas believe it is not important
because they and their neighbors can afford to access resources in
another way.

People in areas with higher ADI tend to have worse health outcomes on
the whole due to low socioeconomic status and lack of access to
healthcare. I was curious if people in these areas used the library to
research health topics more than their low ADI counterparts. Researching
at the library may offer an alternative way to access health
information.

```{r}

plot <- ggplot(atfadi, aes(x=as.factor(S8_31), y=ADI, group=S8_31))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Research health at library', y= 'Area Deprivation Index', title = "ADI by Frequecy of Health Research", caption = "Dataset: atfadi")+
 scale_x_discrete(labels = c('1'= 'Never- 
    not aware of 
    service', '2'='Never', '3'='< Once a 
    year', '4'='Every 6 
    months', "5"= 'Every 2-5
    months', "6"='Once a 
    month', "7"='Every 2-3 
    weeks', "8"='Once a week
    or more'))
plot
```

Those who researched their health at the library the most often tended
to live in areas with higher ADI, again indicating people in these areas
may be more likely to turn to their library for resources they may not
be able to access elsewhere.

\pagebreak

Surprisingly, those in higher ADI areas were slightly more supportive of
cutting public health and public library funding in a budget crisis, but
neither correlation is significant.

```{r}
plot <- ggplot(atfadi, aes(x=as.factor(Q9_2_4), y=ADI, group=Q9_2_4))+
  geom_boxplot(na.rm= TRUE) +
  labs(x='First thing to cut in budget crisis- Public Health', y= 'Area Deprivation Index', title = "Willingness to Cut Public Health Funding by ADI", caption = "Dataset: atfadi") +
    scale_x_discrete(labels = c('1'= '1 Strongly
    Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly 
   Agree"))
plot

cor.test(atfadi$ADI,atfadi$Q9_2_4, 
         alternative="greater", 
         method= "pearson")
```

```{r}
plot <- ggplot(atfadi, aes(x=as.factor(Q9_2_5), y=ADI, group=Q9_2_5))+
  geom_boxplot(na.rm= TRUE) +
  labs(x='First thing to cut in budget crisis- Public Library', y= 'Area Deprivation Index', title = "Willingness to Cut Library Funding by ADI", caption = "Dataset: atfadi")+
    scale_x_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly
    Agree"))
plot

cor.test(atfadi$ADI,atfadi$Q9_2_5, 
         alternative="greater", 
         method= "pearson")
```

# Discussion

A key takeaway from this report is that there are some differences
between how library visitors and non-visitors view their library. People
who visit their library are more openly supportive of it. They have a
more positive attitude toward it. They may even be more willing to
support it financially. This is important to the extent that libraries
may be able to mobilize their patronage to secure more funding.

Some of the analyses presented in this report conflicted with my
expectations. Particularly when it came to ADI, the correlations I
expected simply did not exist. This may have been due to limitations of
the data itself. First, ADI is a broad measure, which seeks to quantify
many other measures of socioeconomic status into one variable. By
simplifying these measures, some of the nuanced ways of quantifying a
community's status are lost. This report also sought to compare
libraries across the US and its territories. There is huge variation
between these communities and how they use their libraries. It is
possible that many of the comparisons made here are confounded by
factors like population size, geographic area covered, and size of
library system. Attempts were made to address these confounds, but there
seemed to be some inconsistencies in data collection. Additionally, this
data included only the zip code of the central library for any given
system. This is an issue for any library system that contains multiple
branches across different zip codes. The comparisons of ADI and other
variables in the PLS dataset do not accurately capture these libraries.

It is also important to consider what has changed since this data was
collected in 2018. Since the COVID-19 pandemic, people's views of
education and public resources have shifted. Libraries have offered more
online services to keep up with shifting usage. It would be very
interesting to compare how their usage and perception has changed.

# Citations

Pelczar, M., Frehill, L. M., Nielsen, E., & Li, J. (2020). Data File
Documentation: Public Libraries in the United States Fiscal Year 2018.
Institute of Museum and Library Services: Washington, D.C.				

OCLC and American Library Association. (2018). From Awareness to
Funding: Voter Perceptions and Supportof Public Libraries in 2018.
Dublin, OH: OCLC. <https://doi.org/10.25333/C3M92X.>

BroadStreet. (2018). Area Deprivation Index (ADI). BroadStreet and
American Community Survey.
