---
title: "Final Project"
output: pdf_document
date: "2023-12-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(DBI)
library(dbplyr)
library(bigrquery)
library(readxl)
library(ggplot2)
library(stringr)
library(stringr)
library(plyr)
library(ggmap)
library(dplyr)
```
https://github.com/rabine13/SURVMETH-727


```{r}
adi <- read_csv("~/Desktop/SURVMETH 727/Final project/mitable.csv")
atf <- read_csv("~/Desktop/SURVMETH 727/Final project/use.miatf.csv")
pls <- read_csv("~/Desktop/SURVMETH 727/Final project/use.mipls.csv")
```

```{r Final merge and clean}
plsadi <- merge(pls, adi, by.x = "ZIP", by.y = "zipcode", all= FALSE)
fullset <- merge(plsadi, atf, by.x = "ZIP", by.y = "ZIPCODE", all = FALSE)

#remove geo_id, description, year

fullset$geo_id <- NULL
fullset$description <- NULL
fullset$year <- NULL

names(plsadi)[34] <- 'ADI'
names(fullset)[31] <- 'ADI'

```

```{r Visits vs ADI}
cor.test(plsadi$ADI,plsadi$VISITS, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=VISITS))+
  geom_point(na.rm= TRUE)
plot + labs(x='area deprivation index', y= 'visits')

#with percent of pop that has visited
plsadi$PERCENT_VISIT <- (plsadi$VISITS/plsadi$POPU_LSA)*100

cor.test(plsadi$ADI,plsadi$PERCENT_VISIT, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=PERCENT_VISIT))+
  geom_point(na.rm= TRUE)
plot + labs(x='area deprivation index', y= 'percent that visited')

#something is up with the VISITS variable... why so many visits!!
```
There is no significant correlation between ADI and visits for libraries surveyed in the Public Library Survey

```{r whether sample member had visited vs adi of their zip}
plot <- ggplot(fullset, aes(x=VISIT, y=ADI, group=VISIT))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='visits', y= 'adi')
```
among sample members of the awareness to funding sample who had visited a library in the past year. ...


```{r Visits vs funding priority}
#do something similar to above but comparing whether they have visited with their willingness to fund
plot <- ggplot(fullset, aes(x=VISIT, y=Q9_1_5, group=VISIT))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='has visited in past year', y= 'Q9_1_5 Top priority allocating tax dollars - Public Library')
```




```{r Hours library is open compared to ADI of its zipcode}

plsadi$HRS_BRANCH <- plsadi$HRS_OPEN/(plsadi$CENTLIB+plsadi$BRANLIB)


cor.test(plsadi$ADI,plsadi$HRS_BRANCH, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=HRS_BRANCH))+
  geom_point(na.rm= TRUE)
plot + labs(x='area deprivation index', y= 'hours open divided by braches')
```


```{r}
#need to weight by number of branches
# divide hours by central+branches
notable <- plsadi %>%
  filter(HRS_BRANCH > 4000)

print(notable)
```


```{r population vs visits}
cor.test(plsadi$POPU_LSA,plsadi$VISITS, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=POPU_LSA, y=VISITS))+
  geom_point(na.rm= TRUE)
plot + labs(x='population of service area', y= 'visits')
```
significant positive correlation
```{r}
#also maybe weight by branches
highvisit <- plsadi %>%
  filter(VISITS > 2000000)

print(highvisit)
```
DPL and KDL are both huge pop and huge visits.. makes sense!

```{r}
plsadi$wifi_visit <- plsadi$WIFISESS/plsadi$VISITS

cor.test(plsadi$ADI,plsadi$wifi_visit, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=wifi_visit))+
  geom_point(na.rm= TRUE)
plot + labs(x='ADI', y= 'Wifi sessions')


cor.test(plsadi$ADI,plsadi$WIFISESS, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=WIFISESS))+
  geom_point(na.rm= TRUE)
plot + labs(x='ADI', y= 'Wifi sessions')
```
```{r}
cor.test(plsadi$ADI,plsadi$SALARIES, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=SALARIES))+
  geom_point(na.rm= TRUE)
plot + labs(x='ADI', y= 'salary per employee')
```

```{r}
plsadi$SALARY_EMP <- plsadi$SALARIES/plsadi$TOTSTAFF

cor.test(plsadi$ADI,plsadi$SALARY_EMP, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=SALARY_EMP))+
  geom_point(na.rm= TRUE)
plot + labs(x='ADI', y= 'salary per employee')
```

```{r}
#bar graph of mea
plot <- ggplot(fullset, aes(x=S8_31, y=ADI, group=S8_31))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='Research health at library', y= 'adi')
```
People in areas with the highest adi researched at levels 3-4
1 Never - I\\\'m not aware of this library service
2 Never - I\\\'m aware of this service but haven\\\'t used it
3 Once a year or less often
4 Once every 6 months
5 Once every 2-5 months
6 Once a month
7 Once every 2-3 weeks
8 Once a week or more often

```{r}
#do bar grapgs with variace bars
meanadi <- mean(fullset$ADI)
plot <- ggplot(fullset, aes(x=Q9_2_4, y=ADI, group=Q9_2_4))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='First thing to cut in budget crisis- Public Health', y= 'adi')
```


```{r}
plot <- ggplot(fullset, aes(x=Q9_2_5, y=ADI, group=Q9_2_5))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='First thing to cut in budget crisis- Public Library', y= 'adi')
```

```{r}
plot <- ggplot(fullset, aes(x=Q14, y=ADI, group=Q14))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='Importance of a strong public library system', y= 'adi')
```
```{r}
cor.test(fullset$Q14, fullset$ADI, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(fullset, aes(x=Q14, y=ADI))+
  geom_point(na.rm= TRUE)
plot + labs(x='Importance of a strong public library system', y= 'ADI')
```
```{r}
#do bar graph of mean
plot <- ggplot(fullset, aes(x=VISIT, y=Q1, group=VISIT))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='Visited in past year', y= 'Overall Impression Local Library')

summary(fullset$Q1)
```
```{r}
#add a cor test
plot <- ggplot(fullset, aes(x=VISIT, y=s6_b, group=VISIT))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='Visited in past year', y= 's6_b I would be willing to pay more in taxes if it meant better funding for the local public library ')

```
```{r}
#do percents
#wtf fix it
plot <- ggplot(fullset, aes(x=SS8, y=VISIT, group=SS8))+
  geom_count(na.rm= TRUE)
plot + labs(x='child', y= 'visit')
```


```{r}
plot <- ggplot(fullset, aes(x=VISIT, y=s6_g, group=VISIT))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='Visited in past year', y= "s6_g I don't support tax increases that fund services I don't use or benefit from")
```
```{r}
plot <- ggplot(fullset, aes(x=s6_b, y=TOTINCM, group=s6_b))+
  geom_point(na.rm= TRUE)
plot + labs(x='s6_b I would be willing to pay more in taxes if it meant better funding for the local public library ', y= 'Total operating revenue')
```
```{r}
plsadi$PERCENT_USRS <- plsadi$REGBOR/plsadi$POPU_LSA *100

cor.test(plsadi$ADI,plsadi$PERCENT_USRS, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=PERCENT_USRS))+
  geom_point(na.rm= TRUE)
plot + labs(x='ADI', y= 'percent of population registered users')


cor.test(plsadi$ADI,plsadi$REGBOR, 
         alternative="greater", 
         method= "pearson")

plot <- ggplot(plsadi, aes(x=ADI, y=REGBOR))+
  geom_point(na.rm= TRUE)
plot + labs(x='ADI', y= 'Registered users')
```


```{r}
ggplot(fullset, aes(as.factor(VISIT), ..count..)) + 
  geom_bar(aes(fill = as_factor(SS3)), position = "dodge")+
  scale_x_discrete(labels = c("0"="No", "1"="Yes"))+
  labs(x='Visited in past year', y= 'Count')+
scale_fill_discrete(name = "Income", labels=c("1 Less than $20K", "2 $20K to $29K", "3 $30K to $39K", "4 $40K to $49K", "5 $50K to $59K", "6 $60K to $74K", "7 $75K to $99K", "8 $100K to $149K", "9 $150K or more"))
```


