---
title: "727 Final Project"
subtitle: "Socioeconomic Influence on the Usage and Perception of Public Libraries"
author: "Sol Rabine"
date: "2023-12-13"
output: pdf_document
references:
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(DBI)
library(plyr)
library(dbplyr)
library(bigrquery)
library(readxl)
library(ggplot2)
library(stringr)
library(stringr)
library(ggmap)
library(dplyr)
```

<https://github.com/rabine13/SURVMETH-727>

```{r}
adi <- read_csv("~/Desktop/SURVMETH 727/Final project/ustable.csv")
atf <- read_csv("~/Desktop/SURVMETH 727/Final project/usatf.csv")
pls <- read_csv("~/Desktop/SURVMETH 727/Final project/uspls.csv")
```

#Github link: <https://github.com/rabine13/SURVMETH-727>

# The Question

## Across the US, libraries are one of the few places that offer their space and resources to the public for free. This project seeks to examine the differences in how libraries are seen and used by theur communities. Given that it is easier than ever to access information from the internet, are libraries still seen as an important hub of knowledge? Do people from different socioeconomic backgrounds view their library differently?

# The data

## Data for this project comes from from three datasets. The first is the 2018 Area Deprivation Index, which I accessed from the Google Bigquery API. The Area Deprivation Index (ADI) is an evaluation of socioeconomic status compiled from multiple measures in the American Community Survey. This dataset contains an ADI measure for 32664 US zip codes.

## Next is the 2018 Public Libraries Survey, a national census of public libraries in the US and its territories. The survey is conducted by the Institute of Museum and Library Services. The survey is administered to central libraries, who report on all the branches in their system. This dataset (pls) contains robust data about a library system's visitors, employment, revenue, use of materials, and more. This data is linked to the address of the central library in each system. This dataset covers 9261 central libraries. I was able to match 7642 to the ADI of their zipcode.

## The last dataset is from a survey called Awareness to Funding: Voter Perceptions and Support of Public Libraries in 2018 (atf). The survey is conducted by OCLC and the American Library Association. This survey covers 2914 individuals across the country and asks questions about their use of libraries, impression of them, and support of them.

## The data has been merged into 4 different datasets to get the most possible cases for comparison. All datasets were merged using zip codes. The datasets are as follows:

### fullset: contains 819 cases matching public library survey, ADI, and awareness to funding data

### plsadi: contains 7642 cases matching public library data with the ADI of the central library's zipcode. Used for comparative measures of ADI with library hours, visitors, wifi usage, and service area population.

### plsatf: contains 997 cases matching individuals in the Awareness to Funding survey with the central library in their zipcode. Used to compare perceptions of libraries with measures of their use.

### atfadi: contains 2642 cases matching individuals in the Awareness to Funding survey with the ADI of their zipcode. Used to compare usage and perceptions of libraries for individuals in communities with different socioeconomic status.

```{r Final merge and clean}
atf$Q1 <- gsub('1 Unsatisfactory', '1', atf$Q1)
atf$Q1 <- as.numeric(atf$Q1)
plsadi <- merge(pls, adi, by.x = "ZIP", by.y = "zipcode", all= FALSE)
plsatf <- merge(pls, atf, by.x = "ZIP", by.y = "ZIPCODE", all = FALSE)
atfadi <- merge(atf, adi, by.x = "ZIPCODE", by.y = "zipcode", all = FALSE)


fullset <- merge(plsadi, atf, by.x = "ZIP", by.y = "ZIPCODE", all = FALSE)

#remove geo_id, description, year

fullset$geo_id <- NULL
fullset$description <- NULL
fullset$year <- NULL

names(plsadi)[35] <- 'ADI'
names(fullset)[32] <- 'ADI'
names(atfadi)[44] <- 'ADI'

```

# Mapping the libraries

## The purple points on the map represent central libraries that were matched to both their ADI and an individual's ATF responses.

## The "green" points on the map represent central libraries that were matched only to ADI.

## The blue points on the map represent libraries in the PLS dataset that were not matched to the other datasets.

I was unable to retrieve map data for Alaska, Hawaii, American Samoa,
Northern Mariana Islands, Guam, Puerto Rico, and US Virgin Islands so
they have been excluded from this map.

```{r}
all_states <- map_data("state")
```

```{r Map comparing libraries in the full dataset and the ATF dataset}
#remove Alaska and Hawaii 
pls_continent <- filter(pls, !(STABR %in% c('AK', 'HI', 'AS', 'MP', 'GU', 'PR', 'VI')))
plsadi_continent <- filter(plsadi, !(STABR %in% c('AK', 'HI', 'AS', 'MP', 'GU', 'PR', 'VI')))
fullset_contient <- filter(fullset, !(STABR %in% c('AK', 'HI', 'AS', 'MP', 'GU', 'PR', 'VI')))
usmap <- ggplot()+
  geom_polygon(data = all_states, aes(x=long, y=lat, group = group), fill = "grey", color = "black") + 
   geom_point(data = pls_continent, aes(x=LONGITUD, y=LATITUDE), color = "blue") +
  geom_point(data = plsadi_continent, aes(x=LONGITUD, y=LATITUDE), color = "darkgreen") + 
  geom_point(data = fullset_contient, aes(x= LONGITUD, y= LATITUDE), color = "purple") 
usmap
 # ggsave("usmap.png", device = "png", width = 5, height = 5)
```

# Exploration

First, I wanted to look for a correlation between population of a
library's service area and the visits per year. This analysis uses just
the PLS data since merging with other datasets reduced the number of
cases.

```{r population vs visits}
plot <- ggplot(pls, aes(x=POPU_LSA, y=VISITS))+
  geom_point(color = "darkgreen", na.rm= TRUE)+ 
  labs(x='Population of Service Area', y= 'visits', title = "Visits by Population of Service Area", caption = "Dataset: PLS")
plot
#ggsave("plot.png", device = "png", width = 8, height = 5)

cor.test(pls$POPU_LSA,pls$VISITS, 
         alternative="greater", 
         method= "pearson")
```

Understandably, there is a significant positive correlation.

```{r}
#also maybe weight by branches
highvisit <- plsadi %>%
  filter(VISITS > 5000000)
```

I next wanted to examine if library visitorship has a correlation with
ADI. I expected that there would be a positive correlation, that
libraries in areas with higher ADI (worse socioeconomic status) would
have more visitors. This analysis uses the ADI and PLS datasets.

```{r Visits vs ADI}
plot <- ggplot(plsadi, aes(x=ADI, y=VISITS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Visits', title = "Visits by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI, plsadi$VISITS, 
         alternative="greater", 
         method= "pearson")
```

There is no significant correlation. I decided to see if there was a
difference if I looked at the percent of population that had visited.

```{r percent Visits vs ADI}
plsadi$PERCENT_VISIT <- (plsadi$VISITS/plsadi$POPU_LSA)*100

plot <- ggplot(plsadi, aes(x=ADI, y=PERCENT_VISIT))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Percent of Population that Visited', title = "Percent Visited by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$PERCENT_VISIT, 
         alternative="greater", 
         method= "pearson")

```

I noticed three outliers that seemed to have a very low population but
high number of visits:

The Lake Minchumina Community Library with a service area population of
9 and 2071 visits in 2018. The Adams-Pratt Oakland County Law Library
with a service area population of 19 and 28700 visits in 2018. The Round
Top Family Library with a service area population of 91 and 24531 visits
in 2018.

I could find no clear reason for the discrepancy so I did the test with
these outliers removed.

```{r}
plsadiclean <- plsadi[-c(7623,2843, 6536),]
plsadiclean$PERCENT_VISIT <- (plsadiclean$VISITS/plsadiclean$POPU_LSA)*100

plot <- ggplot(plsadiclean, aes(x=ADI, y=PERCENT_VISIT))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Percent of Population that Visited', title = "Percent Visited by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$PERCENT_VISIT, 
         alternative="greater", 
         method= "pearson")

```

There still is no significant correlation, but the distribution looks
much better.

Next, I looked at the hours each branch is open, compared to ADI.

```{r Hours library is open compared to ADI of its zipcode}
plsadi$HRS_BRANCH <- plsadi$HRS_OPEN/(plsadi$CENTLIB+plsadi$BRANLIB)
#remove problem cases
plsadiclean <- plsadi[-c(802,1005, 1816, 4124, 4206, 4375, 6680, 6688, 6915, 6918, 6936, 6937, 6938, 6947, 6948, 7023, 5328),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=HRS_BRANCH))+
  geom_point(na.rm= TRUE)
plot + labs(title = "Branch Hours by ADI", x='Area Deprivation Index', y= 'Hours Open Per Branch', caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI, plsadiclean$HRS_BRANCH, 
         alternative="greater",
         method= "pearson")

```

There is no significant correlation.

I next compared the hours each branch is open with the population they
serve.

```{r}
plsadi$HRS_BRANCH <- plsadi$HRS_OPEN/(plsadi$CENTLIB+plsadi$BRANLIB)
#remove problem cases
plsadiclean <- plsadi[-c(802,1005, 1816, 4124, 4206, 4375, 6680, 6688, 6915, 6918, 6936, 6937, 6938, 6947, 6948, 7023, 5328),]

plot <- ggplot(plsadiclean, aes(x=HRS_BRANCH, y=POPU_LSA))+
  geom_point(na.rm= TRUE)
plot + labs(title = "Branch Hours by Population", x='Hours Open Per Branch', y= 'Population Service Area', caption = "Dataset: plsadi")

cor.test(plsadiclean$POPU_LSA, plsadiclean$HRS_BRANCH, 
         alternative="greater",
         method= "pearson")
```

```{r}
notable <- plsadi %>%
  filter(HRS_BRANCH > 6000)
```

There is a weak but significant positive correlation.

Finally, I decided to see if the registered library users correlated
with ADI.

```{r}
plot <- ggplot(plsadi, aes(x=ADI, y=REGBOR))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Registered users', caption = "Dataset: plsadi", title = "Registered Users by ADI")


cor.test(plsadi$ADI,plsadi$REGBOR, 
         alternative="greater", 
         method= "pearson")

plsadi$PERCENT_USRS <- plsadi$REGBOR/plsadi$POPU_LSA *100

plot <- ggplot(plsadi, aes(x=ADI, y=PERCENT_USRS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Percent of Population Registered Users', title = "Percent Registered Users by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$PERCENT_USRS, 
         alternative="greater", 
         method= "pearson")


```

There is no significant correlation with the number of registered users
or the percent that are registered users. The percent of population that
are registered users is frequently over 100%. My assumption is that
these libraries have not removed registrations for people who have moved
or passed away, leading to this overestimation.

Next, we look at wifi use and ADI

```{r}
plot <- ggplot(plsadi, aes(x=ADI, y=WIFISESS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi sessions', title = "Wifi Sessions by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$WIFISESS, 
         alternative="greater", 
         method= "pearson")

plsadi$wifi_visit <- plsadi$WIFISESS/plsadi$VISITS

plot <- ggplot(plsadi, aes(x=ADI, y=wifi_visit))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi Sessions Per Visit', title = "Wifi Sessions Per Visit by ADI", caption = "Dataset: plsadi")

cor.test(plsadi$ADI,plsadi$wifi_visit, 
         alternative="greater", 
         method= "pearson")

```

There was no correlation between wifi use and ADI before weighting by
total visits.

There is a very small but significant positive positive correlation
between ADI and wifi uses per visit. Meaning, as ADI increases, the
number of people who use the wifi during their visit increases. One
possible explanation is that people in people in more deprived areas are
going to the library to use the wifi because they do not have access at
home. This is expected, but I am surprised the correlation was not
stronger.

I noticed that the library with the most wifi sessions per visit was the
Madera County Law Library, with 368.54 wifi uses per visit. This seems
like a reporting error, so I went ahead and excluded it.

```{r}
plsadiclean <- plsadi[-c(7261),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=WIFISESS))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi sessions', title = "Wifi Sessions by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$WIFISESS, 
         alternative="greater", 
         method= "pearson")


plsadiclean$wifi_visit <- plsadiclean$WIFISESS/plsadiclean$VISITS

plot <- ggplot(plsadiclean, aes(x=ADI, y=wifi_visit))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Wifi sessions Per Visit', title = "Wifi Sessions Per Visit by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$wifi_visit, 
         alternative="greater", 
         method= "pearson")

```

Having removed this outlier, the correlation between ADI and Wifi
sessions per visit is slightly larger and more statistically significant

I also wanted to look at the relationship between staff salaries and
ADI. I expected that libraries in areas with higher ADI would pay their
staff less. I removed cases where salaries were reported as 0 or NA.

```{r}
plsadiclean <- plsadi[-c(5424, 7260, 7193, 7363, 7222),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=SALARIES))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Total staff expenditures', title = "Total Staff Expenditures by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$SALARIES, 
         alternative="greater", 
         method= "pearson")
```

Looking at the total staff expenditures, there is no significant
correlation.

Next I divided the total staff expenditures by the number of staff
members to get an average salary per employee. I removed cases that were
0 or NA, and cases where the resulting average was greater than 200,000.

```{r}
plsadi$SALARY_EMP <- plsadi$SALARIES/plsadi$TOTSTAFF
plsadiclean <- plsadi[-c(5424, 7260, 7193, 7363, 7222, 1738),]

plot <- ggplot(plsadiclean, aes(x=ADI, y=SALARY_EMP))+
  geom_point(na.rm= TRUE)
plot + labs(x='Area Deprivation Index', y= 'Salary per employee', title = "Salary Per Employee by ADI", caption = "Dataset: plsadi")

cor.test(plsadiclean$ADI,plsadiclean$SALARY_EMP, 
         alternative="greater", 
         method= "pearson")

```

There is no significant correlation

# Visitors and non visitors

There were much more library visitors than non-visitors in the ATF data

```{r Number of non visitors and visitors in the ATF data}
count(atf, vars = 'VISIT')
```

734 did not visit a library in the past year 2179 did visit a library in
the past year

Looking at the main topic of this report, I was curious if visitorship
varied by ADI.

```{r whether sample member had visited vs adi of their zip}
plot <- ggplot(atfadi, aes(x=as.factor(VISIT), y=ADI, group = VISIT))+
  geom_boxplot(na.rm= TRUE) +
  labs(x='Visited', y= 'Area Deprivation Index', title = "Comparing ADI of Visitors and Non-Visitors", caption = "Dataset: atfadi")+
  scale_x_discrete(labels = c("0" ="No", "1"="Yes"))
plot

```

Comparing the ADI of sample members who reported visiting their library
and those who did not, we see that those who visited tended to live in
areas with a slightly higher ADI.


Despite this, the pattern of incomes for visitors and non-visitors was roughly the same, as shown below:

```{r}
ggplot(atf, aes(as.factor(VISIT))) + 
  geom_bar(aes(fill = as_factor(SS3)), position = "dodge")+
  scale_x_discrete(labels = c("0"="No", "1"="Yes"))+
  labs(x='Visited in Past Year', y= 'Count', title = "Income of ATF Sample Members", caption = "Dataset: atf")+
scale_fill_discrete(name = "Income", labels=c("1 Less than $20K", "2 $20K to $29K", "3 $30K to $39K", "4 $40K to $49K", "5 $50K to $59K", "6 $60K to $74K", "7 $75K to $99K", "8 $100K to $149K", "9 $150K or more"))
```
Next, I wanted to see if the income of individuals in the sample was representative of their area. As shown below, sample members with high income were on average from higher ADI (more deprived) areas. Based on this, it is important to note these sample members may not be representative of other people in their area. 

```{r}

plot <- ggplot(atfadi, aes(x=as.factor(SS3), y=ADI, group=S8_31))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Income', y= 'Area Deprivation Index', caption = "Dataset: atfadi")+
 scale_x_discrete(labels = c("< $20K", "$20K to 
  $29K", "$30K to 
  $39K", "$40K to 
  $49K", "$50K to 
  $59K", "$60K to 
  $74K", "$75K to 
  $99K", "$100K to 
  $149K", "> $150K "))
plot
```


I used just the ATF data for the following analyses to use the most
possible cases.

Visitors tended to have a better impression of their library than
non-visitors.

```{r}
plot <- ggplot(atf, aes(x=as.factor(VISIT), y=as.factor(Q1), group=VISIT))+
  geom_boxplot(na.rm= TRUE) + 
  labs(x='Visited in past year', y= 'Overall Impression Local Library', title = "Impression of Library by Visitorship", caption = "Dataset: atf")+
   scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Unsatisfactory', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 An Excellent Library"))
plot

```
## fix labels here

```{r}
ggplot(atf, aes(as.factor(VISIT))) + 
  geom_bar(aes(fill = as_factor(SS8)), position = "dodge")+
  scale_x_discrete(labels = c("0"="No", "1"="Yes"))+
  labs(x='Visited in past year', y= 'Count')+
scale_fill_discrete(name = "Has children", labels=c("No", "Yes"))
```

Next I compared whether a respondent had visited their library in the
past year with their response to a likert scale asking if the public
library should be a high priority for allocating tax dollars.

```{r Visits vs funding priority}
plot <- ggplot(atf, aes(x=as.factor(VISIT), y=as.factor(Q9_1_5), group=VISIT))+
  geom_boxplot(na.rm= TRUE)+
 labs(x='Visited in past year', y= 'Top priority allocating tax dollars - Public Library', title = "Funding Priority by Visitorship", caption = "Dataset: atf") +
 scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot

#tax <- ggplot(atf, aes(as.factor(VISIT))) + 
  #geom_bar(aes(fill = as.factor(Q9_1_5)))+
 # scale_x_discrete(labels = c("0"="No", "1"="Yes"))+
 # labs(x='Visited in past year', y= 'Count')+
#scale_fill_brewer(palette = "PRGn",name = "Top priority allocating tax dollars - Public Library", labels=c("1 Strongly Disagree", "2", "3", "4", "5", "6", "7", "8", "9", "10 Strongly Agree"))

#print(tax)
#ggsave("tax.png", device = "png", width = 8, height = 5)
```

Those who have visited are much more supportive of allocating tax
dollars to the public library. The mean for visitors is 2 points higher
on the scale than for non visitors.

```{r}
#add a cor test
plot <- ggplot(fullset, aes(x=as.factor(VISIT), y=as.factor(s6_b), group=VISIT))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Visited in past year', y= 'I would be willing to pay more in taxes if it meant 
       better funding for the local public library ')+
  scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot

```

In spite of this result, there was a surprising response to the
following question

```{r}
plot <- ggplot(atf, aes(x=as.factor(VISIT), y=as.factor(s6_g), group=VISIT))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Visited in past year', y= "I don't support tax increases that fund services
       I don't use or benefit from")+
    scale_x_discrete(labels = c("0" ="No", "1"="Yes"))+
  scale_y_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot
```

I next compared these impressions from the ATF data to the ADI.

People in areas with higher ADI tend to have worse health outcomes on
the whole due to lack of access to resources. I was curious if people in
these areas used the library to research health topics more than their
low ADI counterparts. Researching at the library may offer an
alternative way to access health information.

```{r}
#bar graph of mea
plot <- ggplot(atfadi, aes(x=as.factor(S8_31), y=ADI, group=S8_31))+
  geom_boxplot(na.rm= TRUE)+
  labs(x='Research health at library', y= 'Area Deprivation Index')+
 scale_x_discrete(labels = c('1'= '1', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10"))
plot
```

People in areas with the highest adi researched at levels 3-4 Never -
not aware 

2 Never - I\\'m aware of this service but haven\\'t used it 3
Once a year or less often 4 Once every 6 months 5 Once every 2-5 months
6 Once a month 7 Once every 2-3 weeks 8 Once a week or more often

```{r}
#do bar grapgs with variace bars

plot <- ggplot(atfadi, aes(x=as.factor(Q9_2_4), y=ADI, group=Q9_2_4))+
  geom_boxplot(na.rm= TRUE) +
  labs(x='First thing to cut in budget crisis- Public Health', y= 'Area Deprivation Index') +
    scale_x_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot
```

```{r}
plot <- ggplot(atfadi, aes(x=as.factor(Q9_2_5), y=ADI, group=Q9_2_5))+
  geom_boxplot(na.rm= TRUE) +
  labs(x='First thing to cut in budget crisis- Public Library', y= 'Area Deprivation Index')+
    scale_x_discrete(labels = c('1'= '1 Strongly Disagree', '2'='2', '3'='3', '4'='4', "5"= '5', "6"='6', "7"='7', "8"='8', "9"='9', '10'= "10 Strongly Agree"))
plot
```
## move this one up

```{r}
plot <- ggplot(atfadi, aes(x=Q14, y=ADI, group = Q14))+
  geom_boxplot(na.rm= TRUE) + 
  labs(x='Importance of a strong public library system', y= 'Area Deprivation Index')+         scale_x_continuous(breaks=seq(1, 10, by=1))
plot

cor.test(atfadi$Q14, atfadi$ADI, 
         alternative="greater", 
         method= "pearson")
```

```{r}
#revenue per branch
plot <- ggplot(plsatf, aes(x=as.factor(s6_b), y=TOTINCM, group=s6_b))+
  geom_boxplot(na.rm= TRUE)
plot + labs(x='s6_b I would be willing to pay more in taxes if it meant better funding for the local public library ', y= 'Total operating revenue')
```

# Discussion

There are some differences between library visitors and non-visitors

# Limitations
The analysis presented in this project are broad 

 We are only looking at the zip code of the cental branch

this data is from 2020, and things have likely changed since the
pandemic.

ADI is a broad measure
There seem to be some reporting issues within the PLS data

# Citations

Pelczar, M., Frehill, L. M., Nielsen, E., & Li, J. (2020). Data File
Documentation: Public Libraries in the United States Fiscal Year 2018.
Institute of Museum and Library Services: Washington, D.C.

@article{taylor2000does, title={Does internet research work?},
author={Taylor, Humphrey}, journal={International journal of market
research}, volume={42}, number={1}, pages={1--11}, year={2000},
publisher={SAGE Publications Sage UK: London, England} }
